---
title: "Capuchin Home Ranges"
author: "Fernando Campos"
date: "April 9, 2016"
output: 
  html_document:
    toc: true
    toc_float: true
---

******

Source files available on [Github](https://github.com/camposfa/HomeRanges)

[Contact me](mailto:camposfa@gmail.com) if you are interested in the raw data

```{r echo=FALSE}
knitr::opts_chunk$set(fig.path = 'figures/capuchin-home-ranges/', 
               fig.height = 6, 
               fig.width = 12, 
               tidy = FALSE, 
               warning = FALSE,
               cache = TRUE)
knitr::read_chunk('_source/capuchin-home-ranges.R')
knitr::read_chunk('_source/capuchin-hr-models.R')
```

<br>

# Data Prep

## Load Packages
```{r prepare_workspace, message = FALSE, results = 'hide'}
```

<br>

## Location data
We first read the tracking data stored in the file `ranging-waypoints.csv`. This file is not made available here because some of the data belong to other reserchers.
```{r load_data}
```

<br>

Check data and plot researcher contributions
```{r review_data}
```

<br>

Number of points by group and observer
```{r plot_contributions2}
```

<br>

# Home ranges scales

## Time intervals
```{r calculate_intervals}
```

<br>

## Number of locations
```{r calculate_num_locs}
```

<br>

## Filters
Here we remove periods with few locations
```{r apply_num_locs_threshold}
```

<br>

## HR Interval Plots
Plots of seasonal ranges to be included in the study
```{r plot_times, fig.height = 9}
```

<br>
******
<br>

# Predictor variables

<br>

## Group mass
```{r calculate_group_size}
```

<br>

## Available fruit biomass
Full details here: http://people.ucalgary.ca/~facampos/data/fruit/
```{r calculate_fruit}
```

<br>

## Weather data
Full details here: http://people.ucalgary.ca/~facampos/data/weather/
```{r calculate_weather}
```

<br>

## Habitat maps
```{r load_habitat_maps, message = FALSE, results = 'hide'}
```

<br>

# Calculate home ranges
```{r calculate_hr, eval = FALSE}
```

<br>

## Write UD data
```{r write_ud, eval = FALSE}
```

<br>

## Write other HR data
```{r write_hr_data, eval = FALSE}
```

<br>

**********

<br>


# Models
Linear mixed models of home range size and composition

<br>

## Prepare model workspace
```{r prepare_model_workspace, message = FALSE, results = 'hide'}
```


## Load home range data
```{r load_hr_data}
```

<br>

## Models of home range area

### Fit models
```{r area_models}
```

<br>

### Clean up model results for plotting
```{r rename_area_vars}
```

<br>

### Plot results for home range area
```{r plot_area_results}
```

<br>

## Models of home range composition

### Fit models
```{r ndvi_models}
```

<br>

### Clean up model results for plotting
```{r rename_ndvi_vars}
```

<br>

### Plot results for home range composition
```{r plot_ndvi_results}
```

<br>

## Models comparing home range zones

### Fit models
```{r zones_model}
```

<br>

### Clean up model results for plotting
```{r rename_zones_vars}
```

<br>

### Plot results comparing home range zones
```{r plot_zones_results, fig.width = 6}
```

```{r model_cleanup, echo=FALSE, message = FALSE, results = 'hide'}
```
