---
title: "Repeatability of Migration Routes in Moose"
author: "Fernando Campos"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r set_options, echo = FALSE}
library(knitr)
opts_knit$set(root.dir = normalizePath('~/Dropbox/MooseNavigation/'))
opts_chunk$set(fig.path = 'figures/moose-migration-repeatability/',
               fig.height = 8, 
               fig.width = 12, 
               tidy = FALSE, 
               warning = FALSE,
               cache.path = '~/Documents/Projects/MooseNavigation/Cache/',
               cache = TRUE)
read_chunk('~/Dropbox/MooseNavigation/code/moose-tracks-daily.R')
read_chunk('~/Dropbox/MooseNavigation/code/identify-migrants.R')
read_chunk('~/Dropbox/MooseNavigation/code/path-similarity.R')
```

<br>
<hr>
<br>

# Study Objectives

1. Make a descriptive statistical assessment of moose motion during migration.

    - How does the orientation of daily movement steps change change over the annual cycle and in relation to the seasonal migrations?

    - How do step lengths change over the annual cycle and in relation to the seasonal migrations?

2. Quantify repeatibility in the migration paths of moose, focusing on within-individual vs. between-individual variation.


```{r child = '_child/moose-navigation-repeatability/1-descriptive-summary.Rmd'}
```

```{r child = '_child/moose-navigation-repeatability/2-identify-migrants.Rmd'}
```

```{r child = '_child/moose-navigation-repeatability/3-path-similarity.Rmd'}
```